TEMPERATURES AND METALLICITIES OF M DWARFS IN THE APOGEE SURVEY

### 2019-08-21 paper/draft.tex
add uncertainties to tables

As expected, the Toomre diagram in Figure \ref{fig:toomre} shows that higher metallicity sources in the sample are concentrated in low velocity space corresponding roughly to the thin disk population; while the thick disk population contains a higher concentration of lower metallicity sources. Separating the two populations into separate histograms (also shown in Figure \ref{fig:toomre}), we find that thick disk sources are more metal poor than thin disk sources, with the mean $\pm$ standard deviation of $\feh=0.00\pm0.17\,$dex for the thin disk distribution, and $\feh=-0.14\pm0.19\,$dex for the thick disk distribution.
Metallicities of the two populations from ASPCAP show a similar distribution, with the mean $\pm$ standard deviation being $\mh=-0.16\pm0.16\,$dex for thin disk sources and $\mh=-0.23\pm0.17\,$dex for thick disk sources.

@@

\tablecaption{Cannon results for Temperature/Metallicity model; see online journal for full table. \label{table:mann_results}}

@@

\begin{longrotatetable}
\begin{deluxetable*}{ccc|ccc|c}
\tablecaption{Cannon results for Spectral Type model. \label{table:west_results}}
\tabletypesize{\scriptsize}
\tablehead{
\multicolumn{3}{c}{\underline{Designation}} & \multicolumn{3}{c}{\underline{Spectral Type}}
	& \multicolumn{1}{c}{\underline{Model Fit}} \\
	  \colhead{2MASS ID} & \colhead{RA}   & \colhead{DEC}
    & \colhead{Training} & \colhead{Test} & \colhead{LOOCV} 
    & \colhead{Test $\chi^2$}
} 
	\startdata
	2M03114974+0115158 & 47.957262  & 1.254404  & 1          & 0.9       & 1.4        & 78236   \\
	2M03122509+0021585 & 48.104563  & 0.366251  & 7          & 7.3       & 5.5        & 56504   \\
	2M03423963+0012102 & 55.66513   & 0.202859  & 4          & 3.9       & 3.9        & 29598   \\
	2M04262170+1800009 & 66.590421  & 18.000265 & 5          & 5.0       & 5.1        & 14084   \\
	2M09152918+4407461 & 138.871602 & 44.129498 & 3          & 3.6       & 3.7        & 17921   \\
	2M09183649+2207022 & 139.652051 & 22.117298 & 3          & 2.4       & 2.4        & 10591   \\
	2M09332262+2749021 & 143.344279 & 27.817253 & 3          & 2.8       & 2.7        & 17388   \\
	2M09373349+5534057 & 144.389577 & 55.568275 & 6          & 6.5       & 6.4        & 15335   \\
	2M10313413+3441535 & 157.892222 & 34.698212 & 1          & 2.0       & 2.3        & 21134   \\
	2M11194647+0820356 & 169.943658 & 8.343246  & 8          & 7.5       & 6.5        & 37803   \\
	2M11203609+0704135 & 170.1504   & 7.070432  & 6          & 6.1       & 5.9        & 18677   \\
	2M11570299+2028436 & 179.262465 & 20.4788   & 2          & 2.9       & 3.0        & 16205   \\
	2M12203634+2505351 & 185.15143  & 25.093107 & 4          & 3.4       & 3.1        & 85745   \\
	2M12212701-0030560 & 185.362567 & -0.515566 & 0          & 1.4       & 1.8        & 22646   \\
	2M12423245-0646077 & 190.635249 & -6.768827 & 2          & 2.4       & 2.5        & 18410   \\
	2M12464541-0312524 & 191.689212 & -3.214578 & 4          & 3.6       & 3.5        & 11561   \\
	2M12471099+1109566 & 191.795795 & 11.165737 & 3          & 3.1       & 3.0        & 12738   \\
	2M12492657-0312032 & 192.360749 & -3.200903 & 3          & 3.3       & 3.5        & 37756   \\
	2M12503440+4309482 & 192.643353 & 43.163414 & 4          & 4.0       & 4.0        & 19726   \\
	2M12523816+1240586 & 193.159002 & 12.682945 & 4          & 4.1       & 4.1        & 15526   \\
	2M12552141+4150425 & 193.839213 & 41.845161 & 3          & 3.1       & 3.1        & 29274   \\
	2M12564117+4233175 & 194.171558 & 42.554871 & 3          & 3.1       & 3.1        & 35083   \\
	2M13032161+4220407 & 195.840051 & 42.344654 & 2          & 2.7       & 2.8        & 14657   \\
	2M13415860+1852278 & 205.494169 & 18.874393 & 4          & 3.9       & 3.9        & 9475    \\
	2M13442970+5625445 & 206.123779 & 56.429039 & 5          & 5.9       & 6.0        & 16017   \\
	\nodata & \nodata & \nodata & \nodata & \nodata & \nodata & \nodata
	\enddata
\end{deluxetable*}
\end{longrotatetable}

>>>>

As expected, the Toomre diagram in Figure \ref{fig:toomre} shows that higher metallicity sources in the sample are concentrated in low velocity space corresponding roughly to the thin disk population; while the thick disk population contains a higher concentration of lower metallicity sources. Separating the two populations into separate histograms (also shown in Figure \ref{fig:toomre}), we find that thick disk sources are marginally more metal poor than thin disk sources, with the mean $\pm$ standard deviation of $\feh=0.00\pm0.17\,$dex for the thin disk distribution, and $\feh=-0.14\pm0.19\,$dex for the thick disk distribution.
Metallicities of the two populations from ASPCAP show a similar distribution, with the mean $\pm$ standard deviation being $\mh=-0.16\pm0.16\,$dex for thin disk sources and $\mh=-0.23\pm0.17\,$dex for thick disk sources.

@@

\tablecaption{\cannon\ results for Temperature/Metallicity model; see online journal for full table. Reported uncertainties for the M15 training sample labels are $\pm$60\,K/0.08\,dex, and reported uncertainties for \thecannon\ model based on the cross-validation scatter are $\pm$77\,K/0.09\,dex. \label{table:mann_results}}

@@

\begin{longrotatetable}
\begin{deluxetable*}{ccc|ccc|c}
\tablecaption{Cannon results for Spectral Type model. Reported uncertainties for the W11 training sample labels are $\pm$1 spectral types, and reported uncertainties for \thecannon\ model based on the cross-validation scatter are $\pm$0.7 spectral types for types $\leq$M6. \label{table:west_results}}
\tabletypesize{\scriptsize}
\tablehead{
\multicolumn{3}{c}{\underline{Designation}} & \multicolumn{3}{c}{\underline{Spectral Type}}
	& \multicolumn{1}{c}{\underline{Model Fit}} \\
	  \colhead{2MASS ID} & \colhead{RA}   & \colhead{DEC}
    & \colhead{Training} & \colhead{Test} & \colhead{LOOCV} 
    & \colhead{Test $\chi^2$}
} 
	\startdata
	2M03114974+0115158 & 47.957262  & 1.254404  & 1          & 0.9       & 1.4        & 78236   \\
	2M03122509+0021585 & 48.104563  & 0.366251  & 7          & 7.3       & 5.5        & 56504   \\
	2M03423963+0012102 & 55.66513   & 0.202859  & 4          & 3.9       & 3.9        & 29598   \\
	2M04262170+1800009 & 66.590421  & 18.000265 & 5          & 5.0       & 5.1        & 14084   \\
	2M09152918+4407461 & 138.871602 & 44.129498 & 3          & 3.6       & 3.7        & 17921   \\
	2M09183649+2207022 & 139.652051 & 22.117298 & 3          & 2.4       & 2.4        & 10591   \\
	2M09332262+2749021 & 143.344279 & 27.817253 & 3          & 2.8       & 2.7        & 17388   \\
	2M09373349+5534057 & 144.389577 & 55.568275 & 6          & 6.5       & 6.4        & 15335   \\
	2M10313413+3441535 & 157.892222 & 34.698212 & 1          & 2.0       & 2.3        & 21134   \\
	2M11194647+0820356 & 169.943658 & 8.343246  & 8          & 7.5       & 6.5        & 37803   \\
	2M11203609+0704135 & 170.1504   & 7.070432  & 6          & 6.1       & 5.9        & 18677   \\
	2M11570299+2028436 & 179.262465 & 20.4788   & 2          & 2.9       & 3.0        & 16205   \\
	2M12203634+2505351 & 185.15143  & 25.093107 & 4          & 3.4       & 3.1        & 85745   \\
	2M12212701-0030560 & 185.362567 & -0.515566 & 0          & 1.4       & 1.8        & 22646   \\
	2M12423245-0646077 & 190.635249 & -6.768827 & 2          & 2.4       & 2.5        & 18410   \\
	2M12464541-0312524 & 191.689212 & -3.214578 & 4          & 3.6       & 3.5        & 11561   \\
	2M12471099+1109566 & 191.795795 & 11.165737 & 3          & 3.1       & 3.0        & 12738   \\
	2M12492657-0312032 & 192.360749 & -3.200903 & 3          & 3.3       & 3.5        & 37756   \\
	2M12503440+4309482 & 192.643353 & 43.163414 & 4          & 4.0       & 4.0        & 19726   \\
	2M12523816+1240586 & 193.159002 & 12.682945 & 4          & 4.1       & 4.1        & 15526   \\
	2M12552141+4150425 & 193.839213 & 41.845161 & 3          & 3.1       & 3.1        & 29274   \\
	2M12564117+4233175 & 194.171558 & 42.554871 & 3          & 3.1       & 3.1        & 35083   \\
	2M13032161+4220407 & 195.840051 & 42.344654 & 2          & 2.7       & 2.8        & 14657   \\
	2M13415860+1852278 & 205.494169 & 18.874393 & 4          & 3.9       & 3.9        & 9475    \\
	2M13442970+5625445 & 206.123779 & 56.429039 & 5          & 5.9       & 6.0        & 16017   \\
	\nodata & \nodata & \nodata & \nodata & \nodata & \nodata & \nodata
	\enddata
\end{deluxetable*}
\end{longrotatetable}
